Do investors in clean energy ETFs herd?

### 2024-12-22 alt_energy_herding.qmd
new lit

A key feature of the green financial products is the exchange traded funds (ETFs). ETFs are a type of security that involves a collection of securities—such as stocks—that often tracks an underlying index, although they can invest in any number of industry sectors or use various strategies. In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in companies that are environmentally friendly [@briere2023]. Thus, ESG ETFs exhibit environment friendly characteristics.

@@

The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies. There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets \textcolor{red}{(see inter alia….)}. @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.  It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets. Therefore, in the context of our study and following previous studies that study the determinants of herding behaviour [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.

@@

Results of baseline and rolling window analysis points to significant herding for the whole period and in various instances.
\newpage

>>>>

A key feature of the green financial products is the exchange traded funds (ETFs). ETFs are a type of security that involves a collection of securities that often tracks an underlying index, although they can invest in any number of industry sectors or use various strategies. In addition, environment, social, and governance (ESG) ETFs serve as a market discovery tool for investors to identify and invest in companies that are environmentally friendly [@briere2023]. Thus, ESG ETFs exhibit environment friendly characteristics.

@@

The behaviour of participants in energy markets is closely related to the developments in the field of climate risks, carbon emissions  and environmentally friendly policies. There are a few studies that attempt to quantify the effects of uncertainty related to climate on the economy and financial markets. @bua2024 developed two climate risk related indexes namely transition and physical risk using a text-based approach in order to study the effect of these risks in financial markets.  It is expected that investors would prefer to hold assets that perform well in the face of increasing climate change risks, even if this entails accepting lower returns for such climate-hedging assets. Therefore, in the context of our study and following previous studies that study the determinants of herding behaviour [see @bouri2019; @demirer2018], we attempt to study the effect of climate-related uncertainty on the formation of herding behavior in the clean energy market.

@@

Results of baseline and rolling window analysis points to significant herding for the whole period and in various instances.

@choi2023
@kuang2021

### 2024-12-22 alt_energy_herding.tex
new lit

A key feature of the green financial products is the exchange traded
funds (ETFs). ETFs are a type of security that involves a collection of
securities---such as stocks---that often tracks an underlying index,
although they can invest in any number of industry sectors or use
various strategies. In addition, environment, social, and governance
(ESG) ETFs serve as a market discovery tool for investors to identify
and invest in companies that are environmentally friendly
\citep{briere2023}. Thus, ESG ETFs exhibit environment friendly
characteristics.

@@

The behaviour of participants in energy markets is closely related to
the developments in the field of climate risks, carbon emissions and
environmentally friendly policies. There are a few studies that attempt
to quantify the effects of uncertainty related to climate on the economy
and financial markets \textcolor{red}{(see inter alia….)}.
\citet{bua2024} developed two climate risk related indexes namely
transition and physical risk using a text-based approach in order to
study the effect of these risks in financial markets. It is expected
that investors would prefer to hold assets that perform well in the face
of increasing climate change risks, even if this entails accepting lower
returns for such climate-hedging assets. Therefore, in the context of
our study and following previous studies that study the determinants of
herding behaviour \citep[see][]{bouri2019, demirer2018}, we attempt to
study the effect of climate-related uncertainty on the formation of
herding behavior in the clean energy market.

@@

Results of baseline and rolling window analysis points to significant
herding for the whole period and in various instances. \newpage

>>>>

A key feature of the green financial products is the exchange traded
funds (ETFs). ETFs are a type of security that involves a collection of
securities that often tracks an underlying index, although they can
invest in any number of industry sectors or use various strategies. In
addition, environment, social, and governance (ESG) ETFs serve as a
market discovery tool for investors to identify and invest in companies
that are environmentally friendly \citep{briere2023}. Thus, ESG ETFs
exhibit environment friendly characteristics.

@@

The behaviour of participants in energy markets is closely related to
the developments in the field of climate risks, carbon emissions and
environmentally friendly policies. There are a few studies that attempt
to quantify the effects of uncertainty related to climate on the economy
and financial markets. \citet{bua2024} developed two climate risk
related indexes namely transition and physical risk using a text-based
approach in order to study the effect of these risks in financial
markets. It is expected that investors would prefer to hold assets that
perform well in the face of increasing climate change risks, even if
this entails accepting lower returns for such climate-hedging assets.
Therefore, in the context of our study and following previous studies
that study the determinants of herding behaviour
\citep[see][]{bouri2019, demirer2018}, we attempt to study the effect of
climate-related uncertainty on the formation of herding behavior in the
clean energy market.

@@

Results of baseline and rolling window analysis points to significant
herding for the whole period and in various instances.

\citet{choi2023} \citet{kuang2021}
